---
output:
  bookdown::pdf_document2:
    includes:
      in_header: preamble.tex
    toc: FALSE
    highlight: tango
    number_sections: TRUE
    df_print: tibble
    latex_engine: pdflatex
bibliography: [paper.bib, packages.bib]
biblio-style: apalike
urlcolor: black
linkcolor: blue
links-as-notes: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center",
  out.width = "100%", dpi = 300, fig.asp = 0.618, collapse = TRUE
)

devtools::load_all(".")
library(dplyr)

uk_cqr3 <- readr::read_rds(here::here("data_results", "uk_cqr3.rds"))

uk_cqr <- uk_cqr3 |> filter(method %in% c("original", "cqr"))
uk_cqr_asymmetric <- uk_cqr3 |> filter(method %in% c("original", "cqr_asymmetric"))
uk_cqr_multiplicative <- uk_cqr3 |> filter(method %in% c("original", "cqr_multiplicative"))
```

```{r, include=FALSE}
display_table <- function(df, caption, bold_header = TRUE, striped = TRUE) {
  tab <- df |>
    kableExtra::kbl(
      digits = 2, align = "c", booktabs = TRUE, caption = caption
    ) |>
    kableExtra::row_spec(row = 0, bold = bold_header) |>
    kableExtra::kable_styling(position = "center", full_width = FALSE)

  if (striped) {
    tab <- tab |> kableExtra::kable_styling(latex_options = "striped")
  }

  return(tab)
}
```


# Conformalized Quantile Regression {#cqr}

This chapter introduces *Conformalized Quantile Regression (CQR)* as the first of two main post-processing procedures that we implemented in the `postforecasts` package.

\Cref{cqr-traditional} explains the original Conformalized Quantile Regression algorithm as proposed in @romano2019.
There, we highlight potential limitations of the traditional implementation that could potentially be fixed by more flexible modifications, which are discussed in \Cref{cqr-asymmetric} and \Cref{cqr-multiplicative}.

## Traditional CQR {#cqr-traditional}

All derivations in this sections are taken from the original paper [@romano2019].
The authors motivate Conformalized Quantile Regression by stating two criteria that an ideal procedure for generating prediction intervals should satisfy:

- It should provide valid coverage in finite samples without making strong distributional assumptions

- The resulting intervals should be as short as possible at each point in the input space

According to the authors, CQR performs well on both criteria while being *distribution-free* and adaptive to *heteroscedasticity*.

### Statistical Validity

The algorithm that CQR is build upon is statistically supported by the following Theorem:

::: {.theorem #cqr}
If $(X_i, Y_i), i = 1, \ldots, n+1$ are exchangeable, then the $(1 - \alpha) \cdot 100$% prediction interval $C(X_{n+1})$ constructed by the CQR algorithm satisfies
<!--  -->
$$
\begin{aligned}
P \left(Y_{n+1} \in C(X_{n+1}) \right) \geq 1 - \alpha.
\end{aligned}
$$
<!--  -->
Moreover, if the conformity scores $E_i$ are almost surely distinct, then the prediction interval is nearly perfectly calibrated:
<!--  -->
$$
\begin{aligned}
P \left( Y_{n+1} \in C(X_{n+1}) \right) \leq 1 - \alpha + \frac{ 1}{ \left| I_2 \right| + 1}, 
\end{aligned}
$$
<!--  -->
where $I_2$ denotes the calibration set.
:::

Thus, the first statement of \Cref{thm:cqr} provides a coverage *guarantee* in the sense that the adjusted prediction interval is *lower-bounded* by the desired coverage level.
The second statement adds an *upper-bound* to the coverage probability which gets tighter with increasing sample size and asymptotically converges to the desired coverage level $1 - \alpha$ such that lower bound and upper bound are asymptotically identical.


### Algorithm {#algorithm}

The CQR algorithm is best described as a multi-step procedure.

**Step 1:** \
Split the data into a training and validation (here called *calibration*) set, indexed by $I_1$ and $I_2$, respectively.

**Step 2:** \
For a given quantile $\alpha$ and a given quantile regression algorithm $\mathcal{A}$, calculate lower and upper interval bounds on the training set:
<!--  -->
$$
\begin{aligned}
\left\{ \hat{ q}_{\alpha, low}, \; \hat{ q}_{\alpha, high} \right\} \leftarrow \mathcal{A} \left( \left\{ (X_i, Y_i): i \in I_1 \right\} \right). 
\end{aligned}
$$
<!--  -->

**Step 3:** \
Compute *conformity scores* on the calibration set:
<!--  -->
$$
\begin{aligned}
E_i := \operatorname*{max} \left\{ \hat{ q}_{\alpha, low}(X_i) - Y_i, \; Y_i - \hat{ q}_{\alpha, high}(X_i) \right\} \quad \forall \; i \in I_2
\end{aligned}
$$
<!--  -->
For each $i$, the corresponding score $E_i$ is *positive* if $Y_i$ is *outside* the interval $\left[ \hat{ q}_{\alpha, low}(X_i), \; \hat{ q}_{\alpha, high}(X_i) \right]$ and *negative* if $Y_i$ is *inside* the interval.

**Step 4:** \
Compute the *margin* $Q_{1 - \alpha}(E, I_2)$ given by the $(1 - \alpha)(1 + \frac{ 1}{ 1 + \left| I_2 \right| })$-th empirical quantile of the scores $E_i$ in the calibration set.
For small sample sizes and small quantiles $\alpha$ the quantile above can be greater than $1$ in which case it is simply set to $1$ such that the maximum value of the score vector is selected.

**Step 5:** \
On the basis of the original prediction interval bounds $\hat{ q}_{\alpha, low}(X_i)$ and $\hat{ q}_{\alpha, high}(X_i)$, the new *post-processed* prediction interval for $Y_i$ is given by
<!--  -->
$$
\begin{aligned}
C(X_{n+1}) = \left[ \hat{ q}_{\alpha,  low}(X_i) - Q_{1 - \alpha}(E, I_2), \; \hat{ q}_{\alpha,  high}(X_i) + Q_{1 - \alpha}(E, I_2) \right].
\end{aligned}
$$
<!--  -->
Note that the *same* margin $Q_{1 - \alpha}(E, I_2)$ is subtracted from the original lower quantile prediction and added to the original upper quantile prediction.
This limitation is adressed in \Cref{cqr-asymmetric}.



















## Asymmetric CQR {#cqr-asymmetric}

### Theory {#cqr-asymmetric-theory}

As noted in \Cref{cqr-traditional} this section suggests a first extension to the original CQR algorithm.
Instead of limiting ourselves to choose the *same* margin $Q_{1 - \alpha}(E, I_2)$ for adjusting the original lower and upper quantile predictions, we allow for individual and, thus, generally different margins $Q_{1 - \alpha, low}(E, I_2)$ and $Q_{1 - \alpha, high}(E, I_2)$ such that the post-processed prediction interval is given by 
<!--  -->
$$
\begin{aligned}
C(X_{n+1}) = \left[ \hat{ q}_{\alpha, low}(X_i) - Q_{1 - \alpha, low}(E_{low}, I_2), \; \hat{ q}_{\alpha, high}(X_i) + Q_{1 - \alpha, high}(E_{high}, I_2) \right].
\end{aligned}
$$
<!--  -->
This asymmetric version additionally requires a change in the computation of the conformity scores. 
Instead of considering the elementwise maximum of the differences between observed values $Y_i$ and original bounds, we simply compute two separate score vectors:
<!--  -->
$$
\begin{aligned}
E_{i, low} &:= \hat{ q}_{\alpha, low}(X_i) - Y_i \quad \forall \; i \in I_2 \\
E_{i, high} &:= Y_i - \hat{ q}_{\alpha, high}(X_i) \quad \forall \; i \in I_2 
\end{aligned}
$$
<!--  -->


### Results 

To avoid repetitions with respect to \Cref{cqr-traditional} we only briefly mention where asymmetric and vanilla CQR have similar effects and rather focus on the differences.

```{r, ch2-uk-cqr-asym-intervals, echo=FALSE, out.width="80%", fig.cap="Illustration of CQR's slow reaction process"}
mod <- "seabbs"
h <- 2
t <- "Cases"
l <- "GB"
q <- 0.05

plot_intervals(
  uk_cqr_asymmetric,
  model = mod, target_type = t, horizon = h, quantile = q, highlight_time_point = 11
)
```

\Cref{fig:ch2-uk-cqr-asym-intervals} nicely demonstrates the key characteristics of asymmetric CQR: Adjustments of the lower and upper interval bounds are independent from each other.
Considering the last interval on the far right the lower bound is adjusted downwards by a large amount whereas the upper bound is increased only slightly.
This behaviour implies that, in contrast to traditional CQR, original and corrected prediction intervals are generally *not* centered around the same midpoint.

The plot also illustrates what we have already seen in \Cref{cqr-traditional}: 
Once the true value is not contained in the prediction interval and there is a large discrepancy towards the closest boundary, all CQR versions tend to *overcompensate* in the next time step.
This jump can be observed from time step $9$ to time step $10$, where the latter is highlighted by the red dashed line.
Even more problematic, the large correction margin only vanishes very gradually afterwards even if the observed Time Series has stabilized.
In \Cref{fig:ch2-uk-cqr-asym-intervals} the lower quantile prediction of asymmetric CQR approaches the original lower quantile forecast very slowly after the jump in observed Cases.
The following paragraphs aim to explain this inflexibility in detail and draw the connection to the underlying algorithm that was developed ealier in this chapter.

### CQR downsides 

Going back to \Cref{cqr-asymmetric-theory} asymmetric CQR computes two separate score vectors based on the original lower and upper quantile forecasts and the vector of observed values.
To confirm our findings visually we select the data subset of  \Cref{fig:ch2-uk-cqr-asym-intervals}.

Consider the intervals one step prior to the red vertical line.
At this point in time the training set includes the first $9$ elements of true values and predicted quantiles which are then used to compute a list of lower and upper scores:

```{r, include=FALSE}
subset_original <- uk_cqr_asymmetric |> filter(method == "original")
subset_asymmetric <- uk_cqr_asymmetric |> filter(method == "cqr_asymmetric")

quantiles_list <- filter_combination(subset_original, mod, l, t, h, q)
quantiles_list_asymmetric <- filter_combination(subset_asymmetric, mod, l, t, h, q)

quantiles_low <- quantiles_list$quantiles_low
true_values <- quantiles_list$true_values
quantiles_high <- quantiles_list$quantiles_high
```

```{r}
scores_list <- compute_scores_asymmetric(
  true_values[1:9], quantiles_low[1:9], quantiles_high[1:9]
)
scores_list$scores_lower
```

```{r, include=FALSE}
largest_score <- round(scores_list$scores_lower[9], 1)
```

The vector of lower scores is calculated by the difference of true values and lower predicted quantiles at each time step.
Due to the jump from time point $9$ to $10$ the final element of the lower score vector has a large value of `r largest_score`.

Next, the (scalar) lower margin is computed:

```{r, eval=FALSE}
margin <- compute_margin(scores_list$scores_lower, quantile)
margin
```

```{r, echo=FALSE}
margin <- compute_margin(scores_list$scores_lower, 2 * q)
margin
```

Due to the small sample size of $9$ observations and the relatively small quantile level of $0.05$ the margin is simply the *maximum* or $100$% quantile of the lower scores.
The *updated* lower quantile prediction for the $10$th time point is thus the original lower quantile prediction at time point $10$ minus the margin, i.e.

```{r, eval=FALSE}
quantiles_low[10] - margin
```

```{r, echo=FALSE}
(quantiles_low[10] - margin) |>
  unname() |>
  round(2)
```

which coincides with \Cref{fig:ch2-uk-cqr-asym-intervals}.

The procedure now continues by consecutively adding the next elements to the vector of true values and original quantile predictions.
Since the differences in observed incidence of Cases and predicted lower bound are all much *smaller* for the remaining time steps, the **same** value `r largest_score` remains the maximum of the lower score vector until the end!
Thus, if like in the case above, the margin always equaled the maximum score, the adjustments would stay that large independent of the future development of the time series.

In fact, the only difference from that scenario to **Step 4** of \Cref{algorithm} is that the *quantile* of the score vector that determines the value of the margin depends on the *size* of the score vector.
Since the size increases by ine with each time step during the Time Series Cross Validation process, this quantile slowly declines.
For instance, the margin which is responsible for adjusting forcasts at time point $11$ is not simply the maximum anymore:

```{r, eval=FALSE}
scores_list <- compute_scores_asymmetric(
  true_values[1:10], quantiles_low[1:10], quantiles_high[1:10]
)
margin <- compute_margin(scores_list$scores_lower, quantile)
margin
```

```{r, echo=FALSE}
scores_list <- compute_scores_asymmetric(
  true_values[1:10], quantiles_low[1:10], quantiles_high[1:10]
)

margin_lower_original <- compute_margin(scores_list$scores_lower, 2 * q)
margin_lower_original
```

In this case the $99$% quantile is an interpolation of the largest and second largest score, as implemented by the `stats::quantile()` function.

The cycle proceeds in this way until the end.
The conclusion of this brief case study is that all modifications of the traditional CQR algorithm suffer from a slow reaction time towards distribution shifts and particularly sudden jumps within observed values and original forecasts.
This major downside of Conformalized Quantile Regression is an immediate consequence of the **margin** computation which finally determines the magnitude of forecast adjustments.


TODO: Add Global Results that show differences to traditional CQR














## Multiplicative CQR {#cqr-multiplicative}

### Theory {-}

On top of the asymmetric CQR version introduced in \Cref{cqr-asymmetric}, we can extend the CQR algorithm further.
So far, the adjustments to the original prediction interval were always chosen in *additive* form.
It may be useful to leverage the *magnitude* of the original bounds more explicitly by using *relative* or *multiplicative* adjustments.

Hence, we again compute separate margins $Q_{1 - \alpha, low}(E, I_2)$ and $Q_{1 - \alpha, high}(E, I_2)$ which are now *multiplied* with the existing forecasts.
The post-processed prediction interval is then given by
<!--  -->
$$
\begin{aligned}
C(X_{n+1}) = \left[ \hat{ q}_{\alpha, low}(X_i) \cdot Q_{1 - \alpha, low}(E_{low}, I_2), \; \hat{ q}_{\alpha, high}(X_i) \cdot Q_{1 - \alpha, high}(E_{high}, I_2) \right].
\end{aligned}
$$
<!--  -->

Just like the asymmetric version, the computation of the score vectors is changed accordingly to respect the new multiplicative relationship:
<!--  -->
$$
\begin{aligned}
E_{i, low} &:= \frac{ Y_i}{ \hat{ q}_{\alpha, low}(X_i)} \quad \forall \; i \in I_2 \\
E_{i, high} &:= \frac{ Y_i}{ \hat{ q}_{\alpha, high}(X_i)} \quad \forall \; i \in I_2,
\end{aligned}
$$
<!--  -->
where we have to exclude original predictions with the value $0$.
Since in our application of Covid-19 Cases and Deaths all values are non-negative, we threshold the scores at zero such that $E_{i, low}$ equals $0$ whenever $\hat{ q}_{\alpha, low}(X_i) \leq 0$.


### Regularization {-}

While the idea of multiplicative correction terms is appealing, it turns out that the approach above is flawed in two ways:

1.  Recall that the (lower) margin $Q_{1 - \alpha, low}(E, I_2)$ basically *picks* a value of the score vector $E_{low}$ at a given quantile level.
    The score vectors are computed for each combination of *location*, *model*, *target type*, *horizon* and *quantile*, i.e. the number of values in the score vector is identical to the number of distinct time points in the training set.
    For short time series such as our small UK data set, the margin selects the *largest* value in the score vector for small levels of $\alpha$ such as $0.01$ or $0.05$, where each such value represents a *ratio* of observed $Y_i$ and original prediction $\hat{ q}_{\alpha, low}(X_i)$.

    As one might guess, these factors frequently get very large for small initial quantile predictions $\hat{ q}_{\alpha, low}(X_i)$ such that the selected margin for post-processing is unreasonably large.
    In fact, the margin can remain huge if there exists a *single* outlier in the score vector.
    In particular, this naive multiplicative version frequently adjusts the lower quantile prediction to a higher value than its upper quantile counterpart.

    We counteract this extreme sensitivity to outliers by *reducing the spread* inside of the score vector to make it more well behaved. 
    Since we deal with multiplicative factors it makes no sense to standardize them to zero mean and unit variance.
    Instead, we regularize the score vector by pulling all values closer to $1$, while keeping all values nonnegative and respecting their *directions*, i.e. values smaller than $1$ that reduce the interval width keep doing so but to a lesser extent than before and, analogously, prior values greater than one remain to be greater than $1$. 

    This goal is achieved by a *root transformation*.
    Since a greater spread of the score vector should lead to larger regularization we settled on the corrections
    <!--  -->
    $$
    \begin{aligned}
    E_{i, low}^{reg} = E_{i, low}^{ \left( \frac{ 1}{ \sigma_{E_{low}}} \right)}, \quad 
    E_{i, high}^{reg} = E_{i, high}^{ \left( \frac{ 1}{ \sigma_{E_{high}}} \right)},
    \end{aligned}
    $$
    <!--  -->
    where $\sigma_{E}$ denotes the standard deviation of the corresponding score vector.

2.  Chances are high that at least *one* of the original true values $Y_i$ is larger than its corresponding lower quantile prediction $\hat{ q}_{\alpha, low}(X_i)$ such that the maximum of the (regularized) score vector is still larger than $1$.
    Thus, the lower bound for small quantiles $\alpha$ is almost *always* pushed upwards. 
    The same logic applies to the upper bound in which case the entire interval is shifted to the top.
    This behaviour is usually not desired.

    To prevent interval shifts, we add the additional constraint that the lower and upper margin must multiply to $1$, i.e.
    <!--  -->
    $$
    \begin{aligned}
    Q_{1 - \alpha, low} \cdot Q_{1 - \alpha, high} \stackrel{ !}{ =} 1.
    \end{aligned}
    $$
    <!--  -->
    Hence, when the lower bound is adjusted upwards $(Q_{1 - \alpha, low} > 1)$, the upper bound *must* decrease $(Q_{1 - \alpha, high} < 1)$ and the interval becomes smaller.
    Similarly, when the upper bound is adjusted upwards $(Q_{1 - \alpha, high} > 1)$, the lower bound must decrease $(Q_{1 - \alpha, low} < 1)$ leading to larger intervals overall after post-processing.


### Results {-}

As noted in the previous section, *naive* multiplicative Conformalized Quantile Regression without any regularization is useless for post-processing quantile predictions.
Typically, one can observe strong overfitting on the training set such that the training performance indicates promising effects, yet the scores on the validation set are *much* worse than the original forecasts.
Further, the adjusted intervals are shifted upwards and usually too large.

Before numerically evaluating the performance of *regularized* CQR, it is instructive to look at a visual comparison of the original and post-processed forecasts of all three CQR modifications for one specific feature combination, which is shown in \Cref{fig:ch2-uk-cqr3-intervals}. 

```{r, ch2-uk-cqr3-intervals, echo=FALSE, fig.cap="Comparison of CQR variations on the UK data set", out.width="80%"}
plot_intervals(
  df = uk_cqr3, model = "epiforecasts-EpiExpert_direct", target_type = "Cases",
  quantile = 0.2, horizon = 2
)
```

The effect of scaling the score vectors in step $1$ of the regularization procedure and constraining lower and upper margins in the second step can be detected immediately:
Similar to vanilla CQR, the corrected intervals are now centered around the same midpoint as the original forecasts.
In strong contrast to the additive CQR versions, however, the issue of interval explosion has not only been diminished by downscaling the scores, but rather *reversed* such that the interval widths now actually *decreased* at most time points and generally appear too narrow.

```{r, ch2-cqr-mult-training, echo=FALSE}
uk_cqr_multiplicative |>
  extract_training_set() |>
  scoringutils::score() |>
  scoringutils::summarise_scores(by = c("method")) |>
  select(method:overprediction) |>
  display_table(
    caption = "Performance of Multiplicative CQR on the Training Set",
    striped = FALSE
  )
```

Moreover, we no longer have any theoretical guarantees of improved forecasts on the training set since \Cref{thm:cqr} only applies to the original additive and symmetric version of CQR.
This fact is confirmed empirically by \Cref{tab:ch2-cqr-mult-training} which shows the Weighted Interval Score aggregated over all categories of `model`, `target_type`, `horizon` and `quantile`.
Indeed, the multiplicative adjustments result in a slightly worse Weighted Interval Score.

Recall that this behaviour is different from the unregularized version, which performed better than the original forecasts across almost all feature combinations.
On the flipside, the performance on the validation set improved dramatically compared to the naive implementation, even though it does *not* lead to a score improvement in absolute terms as is shown in \Cref{tab:ch2-cqr-mult-validation} separated by the forecasting `model.`
Interestingly, multiplicative CQR indicates the strongest *relative* performance for the `EuroCOVIDhub-baseline` model where the additive CQR algorithms struggle the most.
Overall the score differences across different forecasting models appear to be smoothed out compared to the previous CQR versions which also results from the regularization component that is unique to the multiplicative modification.

```{r, ch2-cqr-mult-validation, echo=FALSE}
uk_cqr_multiplicative |>
  extract_validation_set() |>
  scoringutils::score() |>
  scoringutils::summarise_scores(by = c("method", "model")) |>
  filter(!(model %in% c("epiforecasts-EpiExpert_direct", "epiforecasts-EpiExpert_Rt"))) |>
  select(method:dispersion) |>
  arrange(model) |>
  display_table(caption = "Performance of Multiplicative CQR by Model on the Validation Set")
```

The impression of too narrow adjusted intervals does not generalize to the entire data set.
The `dispersion` column in \Cref{tab:ch2-cqr-mult-validation} shows that the intervals are downsized only for some models such as `epiforecasts-EpiExpert` whereas for others like `epiforecasts-ensemble` the distance between lower and upper bound is larger on average.

```{r, ch2-cqr-mult-dispersion, echo=FALSE}
uk_cqr_multiplicative |>
  extract_validation_set() |>
  scoringutils::score() |>
  scoringutils::summarise_scores(by = c("method", "quantile")) |>
  select(method, quantile, dispersion) |>
  arrange(quantile) |>
  tidyr::pivot_wider(names_from = quantile, values_from = dispersion) |>
  select(method:`0.45`) |>
  display_table(
    caption = "Dispersion of Multiplicative CQR by Quantile on the Validation Set",
    striped = FALSE
  )
```

\Cref{tab:ch2-cqr-mult-dispersion} suggests a connection of the `dispersion` change by multiplicative CQR with the `quantile` level.
Aggregated over all models, target types and horizons the dispersion value is increased by a large amount for extreme quantiles and remains in a similar range to before towards the quantiles in the center of the predictive distribution.
This behaviour is in line with the previously seen additive correction methods and underlines that \Cref{fig:ch2-uk-cqr3-intervals} is not representative for all feature combinations in the UK data set.

Overall, we must conclude that the original CQR algorithm as described in [@romano2019] can *not* be modified towards multiplicative margins in any straightforward way. 
For this reason, we do not extend the analysis of multiplicative CQR to the European Forecast Hub data set and do not include it in the detailed method comparison in \Cref{comparison}. 
