---
title: "Detailed UK-Data Analysis"
author: "Joel Beck"
output:
  bookdown::pdf_document2:
    highlight: tango
    toc: FALSE
    number_sections: FALSE
    df_print: tibble
    latex_engine: pdflatex
    keep_tex: FALSE
  bookdown::html_document2:
    theme: flatly
    highlight: pygments
    toc: TRUE
    toc_float: TRUE
    number_sections: FALSE
    df_print: tibble
urlcolor: blue
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center",
  out.width = "100%", dpi = 300, fig.asp = 0.618, collapse = TRUE
)
```


```{r}
devtools::load_all()
library(patchwork)
library(dplyr)

#uk_combined <- readr::read_rds(here::here("data_results", "uk_cqr.rds"))

#hub_1 <- readr::read_rds(here::here("data_results", "hub_cqr_1.rds"))
#hub_2 <- readr::read_rds(here::here("data_results", "hub_cqr_2.rds"))
#hub_combined <- dplyr::bind_rows(hub_1, hub_2)
```

```{r}
df <- read.csv(here::here("data", "full-data-uk-challenge.csv"))
```

```{r}
model <- "epiforecasts-EpiExpert"
location <- "GB"

#df_list <- update_predictions(df, methods = "qsa_uniform", model, location, cv_init_training = 3)

#df_combined_1 <- collect_predictions(df_list)

# Save an object to a file
#saveRDS(df_combined_1, file = "data_results/uk_qsa_uniform_nopen.rds")

df_combined_1 <- readr::read_rds("data_results/uk_qsa_uniform_nopen.rds")
df_combined_cqr <- readr::read_rds("data_results/uk_cqr.rds")

df_combined_both <- dplyr::full_join(df_combined_1, df_combined_cqr) 
```

# Numerical Analysis

```{r}
df_combined_1 |>
  scoringutils::score() |>
  scoringutils::summarise_scores(by = c("method", "model", "target_type")) |>
  arrange(target_type, desc(method))
```

## analyze Performance on Training and Validation Set separately

```{r}

training_results <- df_combined_1 |>
  extract_training_set() |>
  scoringutils::score() |>
  scoringutils::summarise_scores(by = c("method", "model", "target_type"))
training_results

validation_results <- df_combined_1 |>
  extract_validation_set() |>
  scoringutils::score() |>
  scoringutils::summarise_scores(by = c("method", "model", "target_type"))
validation_results
```

# Graphical Analysis

## for given `model`, `location`, `target_type`, `quantile` and `horizon`

```{r}
#TODO: add the spread factors as attributes to df updated
plot_intervals(df_combined_1, model, location, target_type = "Cases", quantile = 0.05, horizon = 1)
plot_intervals(df_combined_cqr, model, location, target_type = "Cases", quantile = 0.05, horizon = 1)

# not useful right now since true value equals incidences for cqr and absolute cases for qsa
#TODO: The plot below generates weird black lines connecting dots.
plot_intervals(df_combined_both, model, location, target_type = "Cases", quantile = 0.05, horizon = 1)
```

## for given `model`, `location` and `quantile` and different `horizons`

```{r}
plot_intervals_grid(df_combined_1, model, facet_by = "horizon", highlight_cv = TRUE)
```

## for given `model`, `location` and `horizon` and different `quantiles`

```{r}
plot_intervals_grid(df_combined_1, model, facet_by = "quantile", highlight_cv = TRUE)
```

################################################################################################################################################################
# eval
################################################################################################################################################################

# UK Data

## By single category

```{r}
eval_methods(df_combined_1, summarise_by = "model")
eval_methods(df_combined_1, summarise_by = "target_type")
eval_methods(df_combined_1, summarise_by = "horizon")
df_eval <- eval_methods(df_combined_1, summarise_by = "quantile")

plot_eval(df_eval)
plot_eval(df_eval, heatmap = FALSE)
```


## By combination of two categories

```{r}
eval_methods(df_combined_1, summarise_by = c("model", "target_type"))
eval_methods(df_combined_1, summarise_by = c("model", "horizon"))

df_eval <- eval_methods(df_combined_1, summarise_by = c("horizon", "target_type"))
plot_eval(df_eval)
```

## Add marginal relative changes

```{r}
# not really informative, since margins are dominated by category with largest
# values, here "Cases"
# => these margins are almost identical to one row / column of table

# sorted by increasing relative changes
eval_methods(df_combined_1, summarise_by = "model")
eval_methods(df_combined_1, summarise_by = "target_type")

# not sorted by relative changes
df_eval <- eval_methods(
  df_combined_1,
  summarise_by = c("model", "target_type"), margins = TRUE
)
plot_eval(df_eval)
#TODO: why is there an NA in the second row of the heatmap. what is meant by margins, how can the WIS adjust with marginsß
```


## Add 'average' (geometric mean) relative changes of rows and columns

```{r}
df_eval <- eval_methods(
  df_combined_1,
  summarise_by = c("horizon", "target_type"), row_averages = TRUE
)
plot_eval(df_eval)

df_eval <- eval_methods(
  df_combined_1,
  summarise_by = c("horizon", "target_type"), col_averages = TRUE
)
plot_eval(df_eval)

df_eval <- eval_methods(
  df_combined_1,
  summarise_by = c("horizon", "target_type"), row_averages = TRUE,
  col_averages = TRUE
)
plot_eval(df_eval)
#TODO: why do we have an NA in the rows of all these plots? DO we need to clean the data?
```


