---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center",
  out.width = "100%", dpi = 300, fig.asp = 0.618, collapse = TRUE
)

devtools::load_all(".")
library(dplyr)
library(ggplot2)
library(patchwork)

uk_complete <- readr::read_rds(here::here("data_results", "uk_complete.rds"))
```

```{r, include=FALSE}
display_table <- function(df, caption, bold_header = TRUE) {
  tab <- df |>
    kableExtra::kbl(digits = 2, align = "c") |>
    kableExtra::row_spec(row = 0, bold = bold_header) |>
    kableExtra::kable_styling(position = "center", full_width = FALSE)

  return(tab)
}
```

```{r, include=FALSE}
weights_df <- attr(uk_complete, which = "weights")

weights_only <- do.call("rbind", weights_df$weights) |>
  magrittr::set_colnames(value = c(
    "cqr",  "cqr_asymmetric", "qsa_uniform", "qsa_flexible_symmetric",
    "qsa_flexible"
  )) |>
  as_tibble()

weights_full <- bind_cols(
  weights_df |> select(-c(location, weights)),
  weights_only
) |>
  filter(quantile < 0.5) |>
  rowwise() |>
  mutate(rowsum = sum(c_across(cols = cqr:qsa_flexible))) |>
  mutate(max_weight = max(c_across(cols = cqr:qsa_flexible))) |>
  ungroup()
```

# postforecasts

<!-- badges: start -->
<!-- badges: end -->

The goal of `postforecasts` is to unite a variety of post-processing methods into a single easy-to-use interface.

This repository was created in context of the Statistical Practical Training course offered by the Chair of Statistics at the University of Göttingen during Winter Term 2021/22.
If you want to jump straight to the results of our project, please refer to the final course paper `term_paper/Herp_Beck_Post-Processing.pdf` which explains the theory as well as the empirical results of all implemented post-processing methods in great detail.


## Installation

You can install the development version of postforecasts from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nikosbosse/post-processing-forecasts")
```

## Data

The `postforecasts` package is tailored towards post-processing Covid-19 forecasts which are provided by two separate data sets:

### UK Covid-19 Crowd Forecasting Challenge

As part of an ongoing research project by the [EpiForecasts](https://epiforecasts.io/) group at the London School of Hygiene & Tropical Medicine, the *UK Covid-19 Crowd Forecasting Challenge* consisted of submitting weekly predictions of Covid-19 Cases and Deaths in the United Kingdom in $2021$.
The challenge was not restricted to experienced researchers in the field but rather intended to collect quantile predictions for the upcoming four weeks by non-expert individuals.

One of the main motivations was to gather evidence for or against the hypothesis that humans are highly capable of precise *point forecasts*.
Yet, at the same time, they tend to be too confident in their beliefs such that prediction *intervals* are chosen too narrow.
In fact, this tendency presents one motivation for post-processing: Extract valuable information from point forecasts and adjust the corresponding prediction intervals with a systematic correction procedure.

In case of individuals that are unfamiliar with statistical methodology, specifying forecasts for very specific quantiles of the predictive distribution might lead to inconsistencies.
Therefore all participants could determine an uncertainty parameter around their median prediction via an interactive web application such that all quantile predictions could be concluded in an automatic fashion.
Note that this procedure inherently leads to *symmetric* forecast intervals.
The results of the $12$-week challenge are [publicly available](https://epiforecasts.io/uk-challenge/).


### European Covid-19 Forecast Hub

According to their [webpage](https://covid19forecasthub.eu/index.html) the *European Covid-19 Forecast Hub* collects "short-term forecasts of Covid-19 cases and deaths across Europe, created by a multitude of infectious disease modelling teams". 

In contrast to the compact UK data described above, the European Forecast Hub data contains almost two million observations for over $20$ European countries.
Further, the forecasters are knowledgeable research groups that submit their weekly predictions based on statistical models.
Although the data collection continues in regular frequency up to this day, our data set is limited to a $32$-week span from March $2021$ until October $2021$.

The overall structure of the two data sets introduced above is very similar.
Since we will refer to some particularly important columns by name frequently throughout the next chapters, they are briefly described here:

- `location`: The country for which the forecasts were submitted.
Equals `GB` for the UK data. Our analysis for the European Forecast Hub data selects $18$ different European countries.

- `model`: The forecaster (group).
Mostly (non-expert) individuals for the UK data and international research groups for the European Forecast Hub.

- `target_type`: Either Covid-19 Cases or Covid-19 Deaths.

- `horizon`: The time horizon how far in advance the predictions were submitted.
Ranges from $1$ week-ahead to $4$ weeks-ahead.

- `forecast_date`: The exact date when the forecasts were submitted. 

- `target_end_date`: The exact date for which the forecasts were submitted.

- `quantile`: One of $23$ different quantile values ranging from $0.01$ to $0.99$.

- `prediction`: The predicted value for one specific combination of the variables above.

- `true_value`: The actual, observed number of Covid-19 Cases or Deaths. 
This value is repeated $23$ times, once for each quantile value. 


### Weighted Interval Score

In order to quantify if the post-processed prediction intervals improve the original forecasts we chose the *Weighted Interval Score* (WIS) as our evaluation metric.
The WIS is a so-called *Proper Scoring Rule*: It incentivizes the forecaster to state their true best belief and cannot be manipulated in favour of own interests.
It combines measures for interval *sharpness* as well as *overprediction* and *underprediction* and can thus be understood as a trade-off between interval *coverage* and *precision*.

For a rigorous mathematical introduction of the WIS see Section 2.1.3 of our course paper.


## Main Findings

The `postforecasts` package implements three versions for each of two post-processing frameworks: *Conformalized Quantile Regression* (CQR) and *Quantile Spread Averaging* (QSA) as well an as *Ensemble* method, where each quantile prediction is a *convex combination* of the individual methods, i.e. a linear combination where all weights are contained in the unit interval and sum up to one.

This section briefly presents the main findings of comparing all post-processing methods in terms of the Weighted Interval Score for the UK Covid-19 Crowd Forecasting Challenge data set.
Note that only five of the six building block methods are included in the comparison since the *multiplicative CQR* version could not show competitive results early on and is thus omitted.

The data set which contains original and updated forecasts for all post-processing methods for the UK data can be conveniently loaded with the command

```{r, eval=FALSE}
uk_results <- readRDS("data_results/uk_complete.rds")
```

The required computations for obtaining these results can be reproduced with the following commands but may take a lot of computation time:

```{r, eval=FALSE}
library(postforecasts)

uk_data <- readRDS("data_modified/uk_data_incidences.csv")

uk_results <- uk_data |>
  update_predictions(
    methods = c(
      "cqr", "cqr_asymmetric", "qsa_uniform", "qsa_flexible", "qsa_flexible_symmetric"
    ),
    cv_init_training = 0.5
  ) |>
  collect_predictions() |>
  add_ensemble()
```

The following figure provides a visual illustration of original and adjusted prediction intervals of all post-processing methods including the ensemble for one specific combination of the variables `model`, `target_type`, `horizon` and `quantile`.
The color legend displays the ensemble weights for each method: 
In this case only the asymmetric CQR and the flexible (not symmetric) QSA methods contribute to the ensemble.
As a simple weighted average with weights close to $0.5$ the lower (upper) bounds of the ensemble intervals are approximately halfway between the lower (upper) bounds of the `cqr_asymmetric` and `qsa_flexible` intervals.

```{r, echo=FALSE}
mod <- "seabbs"
t <- "Cases"
h <- 4
q <- 0.025

plot_weights <- weights_full |>
  filter(model == mod, target_type == t, horizon == h, quantile == q) |>
  mutate(across(.cols = cqr:qsa_flexible, .fns = ~ round(.x, digits = 4)))

plot_df <- uk_complete |>
  mutate(method = case_when(
    method == "cqr" ~ stringr::str_glue(
      "cqr\nweight: {plot_weights$cqr}"
    ),
    method == "cqr_asymmetric" ~ stringr::str_glue(
      "cqr_asymmetric\nweight: {plot_weights$cqr_asymmetric}"
    ),
    method == "qsa_uniform" ~ stringr::str_glue(
      "qsa_uniform\nweight: {plot_weights$qsa_uniform}"
    ),
    method == "qsa_flexible_symmetric" ~ stringr::str_glue(
      "qsa_flexible_symmetric\nweight: {plot_weights$qsa_flexible_symmetric}"
    ),
    method == "qsa_flexible" ~ stringr::str_glue(
      "qsa_flexible\nweight: {plot_weights$qsa_flexible}"
    ),
    TRUE ~ method
  ))

plot_intervals(
  plot_df,
  model = mod, target_type = t, quantile = q, horizon = h, base_size = 8
) +
  scale_color_manual(
    values = c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00", "#e6ab02", "#a65628")
  )
```

Except for the last observations on the horizontal axis the forecasts of the two CQR versions are quite similar and significantly closer to the original predictions than the QSA intervals. 
Within the QSA family `qsa_flexible` and `qsa_flexible_symmetric` produce almost identical corrections whereas `qsa_uniform` behaves quite differently from all other methods and consistently causes the largest intervals.

The previous figure shows that different methods can have significantly different effects, yet it does not provide any hints which method improves the Weighted Interval Score most.
Thus, the following table collects the WIS for each method on the training and validation set, aggregated over all models, target types, horizons and quantiles and sorted by increasing validation score:

```{r, echo=FALSE}
tab_training <- uk_complete |>
  extract_training_set() |>
  scoringutils::score() |>
  scoringutils::summarise_scores(by = "method") |>
  select(method:dispersion) |>
  rename(`training score` = interval_score)

tab_validation <- uk_complete |>
  extract_validation_set() |>
  scoringutils::score() |>
  scoringutils::summarise_scores(by = "method") |>
  select(method:dispersion) |>
  rename(`validation score` = interval_score)

tab_validation |>
  mutate(`training score` = tab_training$`training score`) |>
  relocate(`training score`, .after = `validation score`) |>
  arrange(`validation score`) |>
  display_table()
```

Based on the table above, our comparison of the `postforecasts` post-processing methods yields a couple of interesting findings:

- All six custom methods improve out-of-sample performance compared to the original predictions on the UK data set.

- All three QSA versions lead to lower validation scores than any CQR variant. 
Thus, based on this first impression, the familiy of QSA post-processing methods clearly outperforms the CQR algorithm for the UK data.

- The ensemble model is the clear winner: 
Combining information from multiple QSA and CQR methods works better on new data than any individual method on its own.
This suggests that the five building block methods are not redundant in the sense that they have different strengths and weaknesses depending on the location in feature space.

- The asymmetric CQR method suffers most from *overfitting* as it results in the lowest training but highest validation score for the small UK data set.

- In general, additional design restrictions such as identical weights in case of `qsa_uniform` and/or the symmetry assumption in case of `cqr` and `qsa_flexible_symmetric` have some kind of *regularization* effect which leads to better generalization to the validation set.
Indeed, the *least* flexible versions of both method frameworks indicate the best validation performance and yet, unsurprisingly, the worst training score.

- All methods improve the original forecasts by *expanding* the prediction intervals which is indicated by the larger *dispersion* values.
`qsa_flexible_symmetric` produces by far the widest intervals on average, yet we can not observe a correlation of better validation scores and either narrower or wider prediction intervals.

## User Guide

This section provides an overview of the most important `postforecasts` functions as as a compact guide how to use our package effectively.

The `postforecasts` functions can be grouped into three categories:

1.  Exploratory

    The `plot_quantiles()`, `plot_intervals()` and `plot_intervals_grid()` functions visualize the development of true Covid-19 Cases and Deaths over time as well as corresponding original and adjusted quantile predictions.

2.  Model Fitting

    The `update_predictions()` function is the workhorse of the entire `postforecasts` package.
    It specifies both the raw data and the post-processing method(s) that should be applied to the data set.
    The function returns a list of $k+1$ equally shaped data frames for $k$ selected post-processing methods where the first element is given by the original, possibly filtered, data frame.

    All list elements can be analyzed separately or collectively by stacking them into one large data frame with the `collect_predictions()` function.
    The combined data frame is designed to work well with analysis functions of the [scoringutils](https://epiforecasts.io/scoringutils/) package.
    If multiple post-processing methods are applied, an ensemble model of all selected methods can be added via the `add_ensemble()` function, which lets the user access both the weighted ensemble predictions and a data frame with the corresponding weights.

3.  Evaluation

    As noted above the Weighted Interval Score is our primary metric to evaluate the *quality* of prediction intervals.
    The `score()` function of the `scoringutils` package computes this quantity for each observation in the data set which can then be aggregated by the related `summarise_scores()` function.
    
    Depending on the *granularity* of the aggregation the output might contain many interval scores of vastly different magnitudes.
    To simplify interpretation the `eval_methods()` function computes *relative* or *percentage* changes in the Weighted Interval Score for each selected method compared to the original quantile predictions.
    Further, these relative changes can be visualized by the `plot_eval()` function.
