---
title: "Testing WIS Functions"
author: "Matthias Herp"
output:
  bookdown::html_document2:
    theme: flatly
    highlight: pygments  # kate
    toc: TRUE
    toc_float: TRUE
    toc_depth: 2
    number_sections: FALSE
    df_print: tibble
  bookdown::pdf_document2:
    highlight: tango  # pygments
    toc: FALSE
    number_sections: FALSE
    df_print: tibble
    latex_engine: pdflatex
    keep_tex: FALSE
urlcolor: blue
editor_options: 
  chunk_output_type: inline
---

```{r knitr-opts, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center",
  out.width = "100%", dpi = 300, fig.asp = 0.618, collapse = TRUE
)
```

```{r libraries, include=FALSE}
devtools::load_all(".")
library(scoringutils)
library(dplyr)
library(patchwork)
library(ggplot2)
```

```{r libraries, include=FALSE}
df <- read.csv(here::here("data_modified", "hub_data_2_incidences.csv"))
m <- "epiforecasts-EpiExpert"
l <- "GB"
t <- "Cases"
h <- 1
```

## Wis calculation

We define two functions that calculate the WIS depending on a quantile spread adjustment for two quantiles. wis_calc is written custom while wis_calc_pac uses the scoring utiles package the WIS.

```{r libraries, include=FALSE}
wis_calc <- function(x_vec = seq(0,3,0.1),
                     qs = c(0.25, 0.5, 0.75),
                     true_values_new = c(rep(50,4), 60, rep(20,5))){
  
  wis_vec <- c()
  for (x in x_vec){
    l <- qs[1] * 100 +  (qs[1]-qs[2])*100 * (x - 1)
    u <- qs[3] * 100 +  (qs[3]-qs[2])*100 * (x - 1)
    m <- qs[2] * 100
    a <- qs[3] - qs[1]
    
    sharp <- length(true_values_new) * abs(u-l) #length(true_values_new) * 
    under <- 0
    over <- 0
    med <- 0
    
    for (obs in true_values_new){
      #if (obs > l && obs < u){
      #  wis_val <- wis_val #+ min(obs-l,u-obs)
      if (obs > l && obs > u){
        over <- over + 2/a + (obs-u)
      } else if (obs < l && obs < u) {
        under <- under + 2/a* (l-obs)
      }
      #add median term
      med <- med + abs(obs-m)
    }
    wis_val <- (1 / (2 + 0.5)) * (1/2 * med + a/2 * (sharp+over+under))
    wis_vec <- c(wis_vec,wis_val)
  }
  
  return(wis_vec)
}
```

```{r libraries, include=FALSE}
wis_calc_pac <- function(x_vec = seq(-2,2,0.1),
                     qs = c(0.25, 0.5, 0.75),
                     true_values_new = c(rep(50,4), 60, rep(20,5)),
                     df = df,
                     m = m,
                     l = l,
                     t = t,
                     h = h){
  

  # Get a subset of original data as template 
  # We only make it have the length of the true values (max remains 25)
  subset <- dplyr::filter(df, model == m & location == l 
                          & target_type == t & horizon == h 
                          & quantile %in% qs 
                          & target_end_date %in% sort(unique(df$target_end_date))[0:length(true_values_new)])
  
  # Changing the quantile predictions to the value of the quantile * 100 * error_factor
  subset_generated <- subset
  for (qi in qs) {
    subset_generated <- subset_generated |>
      dplyr::mutate(prediction = replace(
        .data$prediction, .data$quantile == qi,
        values = rep(qi * 100,length(unique(subset$target_end_date)))
      ))
  }
  
  # Changing the true values at each time point (for each quantile the same)
  for (i in seq(1,length(unique(subset_generated$target_end_date))) ) {
    date <- unique(subset_generated$target_end_date)[i]
    value <- true_values_new[i]
    
    subset_generated <- subset_generated |>
      dplyr::mutate(true_value = replace(
        .data$true_value, .data$target_end_date == date,
        values = rep(value,length(unique(subset_generated$quantile)))
      ))
  }
  
  # adjustment based on x value e.g. line search
  wis_vec <- c()
  for (x in x_vec){
    subset_generated <- subset_generated |>
      dplyr::mutate(prediction = replace(
        .data$prediction, .data$quantile == qs[1],
        values = rep(qs[1] * 100 + (qs[1]-qs[2])*100 * (x-1),length(unique(subset$target_end_date)))
      ))
    subset_generated <- subset_generated |>
      dplyr::mutate(prediction = replace(
        .data$prediction, .data$quantile == qs[3],
        values = rep(qs[3] * 100 + (qs[3]-qs[2])*100 * (x-1),length(unique(subset$target_end_date)))
      ))
    
    res <- subset_generated |>
      scoringutils::score() |>
      scoringutils::summarise_scores(by = c("location"))

    wis_val <- res$interval_score
    wis_vec <- c(wis_vec,wis_val)
    
  }
  return(wis_vec)
}

```

## WIS depending on interval score adjustment

We see that both the custom and the soring utils based WIs calculation give the same minimum value are allthough they have different values as the package version is multiplied by a constant.

```{r}
x <- seq(0,2,0.1)
y <- wis_calc(x,
              qs = c(0.25, 0.5, 0.75),
              true_values_new = c(rep(50,4), 60, rep(20,5)))

df_xy <- data.frame(x = x, y = y)

ggplot() +
  geom_line(data = df_xy, aes(x, y), colour = "black")

```

```{r}
x <- seq(0,2,0.1)
y <- wis_calc_pac(x,
              qs = c(0.25, 0.5, 0.75),
              true_values_new = c(rep(50,4), 60, rep(20,5)))

df_xy <- data.frame(x = x, y = y)

ggplot() +
  geom_line(data = df_xy, aes(x, y), colour = "black")

```

We also show an example of quantiles that give the same WIS. This is due to the tradeoff between underprediction and sharpness which is 50/50 for the intervall covering 50% of the true values.

```{r}
#subset_generated is sorted

x <- unique(subset_generated$target_end_date)

y25 <- dplyr::filter(subset_generated, quantile==0.25)$prediction
y50 <- dplyr::filter(subset_generated, quantile==0.5)$prediction
y75 <- dplyr::filter(subset_generated, quantile==0.75)$prediction
obs <- dplyr::filter(subset_generated, quantile==0.75)$true_value

df_xy <- data.frame(x = x, y25 = y25, y50 = y50, y75 = y75, obs = obs)

ggplot() +
  geom_line(data = df_xy, aes(x, y25, group = 1), colour = "red") +
  geom_line(data = df_xy, aes(x, y50, group = 2), colour = "red") +
  geom_line(data = df_xy, aes(x, y75, group = 3), colour = "red") +
  geom_line(data = df_xy, aes(x, obs, group = 4), colour = "black")

```

```{r}
x = 0.4

subset_generated_updated <- subset_generated |>
      dplyr::mutate(prediction = replace(
        .data$prediction, .data$quantile == qs[1],
        values = rep(qs[1] * 100 + (qs[1]-qs[2])*100 * (x-1),length(unique(subset$target_end_date)))
      ))
subset_generated_updated <- subset_generated_updated |>
      dplyr::mutate(prediction = replace(
        .data$prediction, .data$quantile == qs[3],
        values = rep(qs[3] * 100 + (qs[3]-qs[2])*100 * (x-1),length(unique(subset$target_end_date)))
      ))
    
res <- subset_generated_updated |>
      scoringutils::score() |>
      scoringutils::summarise_scores(by = c("location"))

print(res$interval_score)


x <- unique(subset_generated_updated$target_end_date)

y25 <- dplyr::filter(subset_generated_updated, quantile==0.25)$prediction
y50 <- dplyr::filter(subset_generated_updated, quantile==0.5)$prediction
y75 <- dplyr::filter(subset_generated_updated, quantile==0.75)$prediction
obs <- dplyr::filter(subset_generated_updated, quantile==0.75)$true_value

df_xy <- data.frame(x = x, y25 = y25, y50 = y50, y75 = y75, obs = obs)

ggplot() +
  geom_line(data = df_xy, aes(x, y25, group = 1), colour = "red") +
  geom_line(data = df_xy, aes(x, y50, group = 2), colour = "red") +
  geom_line(data = df_xy, aes(x, y75, group = 3), colour = "red") +
  geom_line(data = df_xy, aes(x, obs, group = 4), colour = "black")


```

```{r}
x = 0.5

subset_generated_updated <- subset_generated |>
      dplyr::mutate(prediction = replace(
        .data$prediction, .data$quantile == qs[1],
        values = rep(qs[1] * 100 + (qs[1]-qs[2])*100 * (x-1),length(unique(subset$target_end_date)))
      ))
subset_generated_updated <- subset_generated_updated |>
      dplyr::mutate(prediction = replace(
        .data$prediction, .data$quantile == qs[3],
        values = rep(qs[3] * 100 + (qs[3]-qs[2])*100 * (x-1),length(unique(subset$target_end_date)))
      ))
    
res <- subset_generated_updated |>
      scoringutils::score() |>
      scoringutils::summarise_scores(by = c("location"))

print(res$interval_score)


x <- unique(subset_generated_updated$target_end_date)

y25 <- dplyr::filter(subset_generated_updated, quantile==0.25)$prediction
y50 <- dplyr::filter(subset_generated_updated, quantile==0.5)$prediction
y75 <- dplyr::filter(subset_generated_updated, quantile==0.75)$prediction
obs <- dplyr::filter(subset_generated_updated, quantile==0.75)$true_value

df_xy <- data.frame(x = x, y25 = y25, y50 = y50, y75 = y75, obs = obs)

ggplot() +
  geom_line(data = df_xy, aes(x, y25, group = 1), colour = "red") +
  geom_line(data = df_xy, aes(x, y50, group = 2), colour = "red") +
  geom_line(data = df_xy, aes(x, y75, group = 3), colour = "red") +
  geom_line(data = df_xy, aes(x, obs, group = 4), colour = "black")


```


### Unanswered Question: Why are the two plots below for the two different computations now very different for a smaller intervall size?

```{r}
x <- seq(0,2,0.1)
y <- wis_calc(x,
              qs = c(0.3, 0.5, 0.7),
              true_values_new = c(rep(50,4), 60, rep(20,5)))

df_xy <- data.frame(x = x, y = y)

ggplot() +
  geom_line(data = df_xy, aes(x, y), colour = "black")

```

```{r}
x <- seq(0,2,0.1)
y <- wis_calc_pac(x,
              qs = c(0.3, 0.5, 0.7),
              true_values_new = c(rep(50,4), 60, rep(20,5)))

df_xy <- data.frame(x = x, y = y)

ggplot() +
  geom_line(data = df_xy, aes(x, y), colour = "black")

```
