---
title: "CQR, CQR Asymmetric & CQR Multiplicative Results"
author: "Joel Beck"
output:
  bookdown::html_document2:
    theme: flatly
    highlight: pygments  
    toc: TRUE
    toc_float: TRUE
    toc_depth: 2
    number_sections: FALSE
    df_print: tibble
  bookdown::pdf_document2:
    highlight: tango
    toc: FALSE
    number_sections: FALSE
    df_print: tibble
    latex_engine: pdflatex
    keep_tex: FALSE
urlcolor: blue
editor_options: 
  chunk_output_type: console
---

```{r knitr-opts, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center",
  out.width = "100%", dpi = 300, fig.asp = 0.618, collapse = TRUE
)
```

```{r libraries}
devtools::load_all(".")
library(dplyr)
```

```{r}
uk_cqr3 <- readr::read_rds(here::here("data_results", "uk_cqr3.rds"))

uk_cqr <- uk_cqr3 |> filter(method %in% c("original", "cqr"))
uk_cqr_asymmetric <- uk_cqr3 |> filter(method %in% c("original", "cqr_asymmetric"))
uk_cqr_multiplicative <- uk_cqr3 |> filter(method %in% c("original", "cqr_multiplicative"))
```

```{r}
uk_cqr_asymmetric |>
  extract_training_set() |>
  scoringutils::score() |>
  scoringutils::summarise_scores(by = c("method", "model")) |>
  select(method:dispersion) |>
  arrange(model)
```

```{r}
uk_cqr_asymmetric |>
  extract_validation_set() |>
  scoringutils::score() |>
  scoringutils::summarise_scores(by = c("method", "model")) |>
  select(method:dispersion) |>
  arrange(model)
```


# CQR Asymmetric

Intervals can get shifted in space for asymmetric version, adjustments to lower bound tend to be stronger than to upper bound.

```{r}
q <- 0.05


plot_intervals(uk_cqr_asymmetric,
  model = "epiforecasts-EpiExpert", target_type = t,
  horizon = h, quantile = q
)
```


large adjustments to lower bound for `seabbs` model.
Note again slow adaptation to lower uncertainty at the end

Consider situation at data point 9 => dashed red line

```{r}
h <- 2
t <- "Cases"
l <- "GB"
q <- 0.05
plot_intervals(uk_cqr_asymmetric,
  model = "seabbs", target_type = t,
  horizon = h, quantile = q, highlight_time_point = 11
)
```


## Case Study

Analyze jump in lower quantile prediction from 9th to 10th data point

```{r}
# all for original method
mod <- "seabbs"

subset_original <- uk_cqr_asymmetric |> filter(method == "original")
subset_asymmetric <- uk_cqr_asymmetric |> filter(method == "cqr_asymmetric")

quantiles_list_original <- filter_combination(subset_original, mod, l, t, h, q)
quantiles_list_asymmetric <- filter_combination(subset_asymmetric, mod, l, t, h, q)

quantiles_low_original <- quantiles_list_original$quantiles_low
true_values_original <- quantiles_list_original$true_values
quantiles_high_original <- quantiles_list_original$quantiles_high
```

Large discrepancy between true value and lower quantile prediction for 9th data point.
Thus large positive score of $415$, which is also chosen as the margin (maximum of lower socres vector is selected for $q = 0.05$).

```{r}
# code of cqr_multiplicative
scores_list_original <- compute_scores_asymmetric(
  true_values_original[1:9], quantiles_low_original[1:9], quantiles_high_original[1:9]
)

# quantiles_low_original - true_values_original
scores_list_original$scores_lower

margin_lower_original <- compute_margin(scores_list_original$scores_lower, 2 * q)
margin_lower_original
```

Thus, updated lower quantile prediction for time point 10 is original lower bound at time point 10 = 336 - margin_lower = 415 = updated lower bound = -79

```{r}
# cqr_asymmetric method

# can contain lower quantile predictions of 0
quantiles_low_asymmetric <- quantiles_list_asymmetric$quantiles_low
true_values_asymmetric <- quantiles_list_asymmetric$true_values
quantiles_high_asymmetric <- quantiles_list_asymmetric$quantiles_high

quantiles_low_original[10] - margin_lower_original
quantiles_low_asymmetric[10]
```


## Effect of large adjustment of lower bound continues for further data points

Now consider situation at data point 10

```{r}
# code of cqr_multiplicative
scores_list_original <- compute_scores_asymmetric(
  true_values_original[1:10], quantiles_low_original[1:10], quantiles_high_original[1:10]
)

# quantiles_low_original - true_values_original
scores_list_original$scores_lower

margin_lower_original <- compute_margin(scores_list_original$scores_lower, 2 * q)
margin_lower_original
```

time series is one observation longer => $99$% quantile is selected
**lower margin is now 383, computation is still dominated by large score of 415 at time point 9** => all further adjustments are dominated by single time point that creates a large margin

```{r}
quantiles_low_original[11] - margin_lower_original
quantiles_low_asymmetric[11]
```

Now consider situation at data point 11

```{r}
# code of cqr_multiplicative
scores_list_original <- compute_scores_asymmetric(
  true_values_original[1:11], quantiles_low_original[1:11], quantiles_high_original[1:11]
)

# quantiles_low_original - true_values_original
scores_list_original$scores_lower

margin_lower_original <- compute_margin(scores_list_original$scores_lower, 2 * q)
margin_lower_original
```

**lower margin now 350** => all further adjustments are dominated by single time point that creates a large margin, magnitude of correction only slowly decreases due to larger number of observations => margin is computed based on a lower quantile of the scores vector

```{r}
quantiles_low_original[12] - margin_lower_original
quantiles_low_asymmetric[12]
```



## Global Evaluation

```{r}
df_eval_horizon <- eval_methods(uk_cqr_asymmetric, summarise_by = c("model"))
plot_eval(df_eval_horizon, heatmap = FALSE)
```


```{r}
uk_cqr_asymmetric_filtered <- uk_cqr_asymmetric |>
  filter(model != "EuroCOVIDhub-baseline")

df_eval_horizon <- eval_methods(
  uk_cqr_asymmetric_filtered,
  summarise_by = c("model", "horizon")
)
plot_eval(df_eval_horizon)
```

```{r}
df_eval_horizon <- eval_methods(
  uk_cqr_asymmetric_filtered,
  summarise_by = c("model", "target_type")
)
plot_eval(df_eval_horizon)
```

```{r}
df_eval_horizon <- eval_methods(
  uk_cqr_asymmetric_filtered,
  summarise_by = c("model", "quantile")
)
plot_eval(df_eval_horizon)
```

```{r}
df_eval_horizon <- eval_methods(
  uk_cqr_asymmetric_filtered,
  summarise_by = c("target_type", "quantile")
)
plot_eval(df_eval_horizon)
```

```{r}
df_eval_horizon <- eval_methods(
  uk_cqr_asymmetric_filtered,
  summarise_by = c("horizon", "quantile")
)
plot_eval(df_eval_horizon)
```

```{r}
df_eval_horizon <- eval_methods(
  uk_cqr_asymmetric_filtered,
  summarise_by = c("horizon", "target_type")
)
plot_eval(df_eval_horizon)
```
