---
title: "Post-Processing COVID-19 Forecasts"
subtitle: "- Second Presentation -<br><br>"
author: "Matthias Herp & Joel Beck"
date: "10.12.2021"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current% / %total%"
      beforeInit: "https://platform.twitter.com/widgets.js"
      # List of highlighting styles: https://highlightjs.org/static/demo/
      # not all of them work with xaringan
      highlightStyle: github
      highlightLines: true
      highlightSpans: true
      ratio: 16:9
      countIncrementalSlides: false
    # Adds logo to all slides except title slide
    # set slide class 'hide_logo' to hide logo on particular slides
    # modify insert-logo.html file with correct file path to logo and desired 
    # logo position 
    # https://www.garrickadenbuie.com/blog/xaringan-tip-logo-all-slides/
    # includes:
    #   after_body: insert-logo.html
---
<!-- here classes for second slide -->

```{r, child="xaringan-setup.Rmd", echo=FALSE}

```

```{r, include=FALSE}
devtools::load_all(".")
library(dplyr)
library(patchwork)

uk_cqr <- readr::read_rds(here::here("data_results", "uk_cqr.rds"))
hub_1 <- readr::read_rds(here::here("data_results", "hub_cqr_1.rds"))
hub_2 <- readr::read_rds(here::here("data_results", "hub_cqr_2.rds"))
hub_cqr <- dplyr::bind_rows(hub_1, hub_2)

uk_cqr_qsa_ensemble <- readr::read_rds(
  here::here("data_results", "uk_cqr_qsa_uniform_ensemble.rds"))
hub_cqr_qsa_ensemble <- readr::read_rds(
  here::here("data_results", "hub_cqr_qsa_uniform_ensemble_subset.rds"))
```

<!-- here content of second slide -->

## Setting

- Post-Processing Covid19 forecasts: Systematically adjust existing prediction intervals with the goal of better out-of-sample performance

--

- Original forecasts from two data sources: The **UK Covid-19 Crowd Forecasting Challenge**<sup>1</sup> (includes forecasts of non-expert individuals) and the **European Forecast Hub**<sup>2</sup> (includes forecasts from international research groups)

.footnote[ 
[1] https://www.crowdforecastr.org/2021/05/11/uk-challenge/ <br>
[2] https://covid19forecasthub.eu/index.html
]

--

- The Quality of prediction intervals is measured by the **Weighted Interval Score** based on a trade-off between interval coverage and precision  

---

## CQR for UK Data

 

---
class: inverse, center, middle

# Quantile Spread Averaging (QSA)

---

## QSA - Theory



---

## QSA - Application



---
class: inverse, center, middle

# Ensemble Model

---

## Ensemble - Idea

- Find the best **convex combination** of post-processed predictions that minimizes the sum of squared residuals 

--

- Averages of independent prediction algorithms often lead to better performance than each individual predictor

---

## Ensemble - Exact Formulation

Consider one particular covariate combination of **model**, **location**, **horizon**, **target type** and **quantile**.

--

Let $n$ specify the number of observations in the training set within this combination, $\mathbf{y} \in \mathbb{R}^n$ the vector of true values and $\hat{\mathbf{y}}_1, \ldots, \hat{\mathbf{y}}_k \in \mathbb{R}^n$ vectors of adjusted predictions from $k$ different post-processing procedures.

--

Then, for each such combination, the ensemble model computes weights $\mathbf{w}^* \in [0, 1]^k$ (technically $\mathbf{w}_{m, l, h, t, q}^*$) by solving the following constrained optimization problem:
$$
\begin{aligned}
\mathbf{w}^*
= \operatorname*{arg\,min}_{ \mathbf{w} \in [0, 1]^k} \left \Vert \mathbf{y} - \sum_{j=1}^{k} w_j \hat{\mathbf{y}}_j \right \Vert_2^2
&= \operatorname*{arg\,min}_{ \mathbf{w} \in [0, 1]^k} \sum_{i=1}^{n} \left(y_i - \sum_{j=1}^{k} w_j \hat{y}_{ij} \right)^2 \\
\text{s.t.} \qquad \sum_{j=1}^{k} w_j &= 1
\end{aligned}
$$
---

## Ensemble - Exact Formulation

Since we only consider the **CQR** and **QSA Uniform** methods in this case, the minimization objective above simplifies to
$$
\begin{aligned}
\mathbf{w}^*
= \begin{pmatrix} w_1^* & w_2^* \end{pmatrix}^T
= \operatorname*{arg\,min}_{w_1, w_2 \in [0, 1]} \sum_{i=1}^{n} \left(y_i - w_1 cqr_i - w_2 qsa_i \right)^2.
\end{aligned}
$$
--

The optimization is implemented with the **quadprog**<sup>1</sup> package which can also be used for more general quadratic programming problems.

.footnote[ 
https://cran.r-project.org/web/packages/quadprog/index.html
]

---

## Comparison of CQR, QSA and Ensemble

---
class: center, middle, inverse

# Outlook

---

## More Methods

- Stable package infrastructure that generalizes well to further Post-Processing methods 

--

- Candidate methods: **Quantile Regression Averaging** and modified versions of CQR 

--

- Comprehensive analysis of strength and weaknesses of each method 

